Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists

### 2024-03-01 paper.Rmd
minor edits

We had help from many people during the various workshops and we would like to thank them for their help (in alphabetical order of their first name): Adéla Sobotkova, Alice Overgaauw, Eduardo Herrera Malatesta, Jens Emil Bødstrup Christoffersen, Johan Broersma, Magnus Lindholm Nielsen, Mandy Hazenberg, María Coto Sarmiento, Paulina Fulneczek, Petra Hermankova, Ties Heesink. We also want to thank all the participants of our workshops.

>>>>

We had help from many people during the various workshops and we would like to thank them for their help (in alphabetical order of their first name): Adéla Sobotkova, Agnes Schneider, Alice Overgaauw, Eduardo Herrera Malatesta, Jens Emil Bødstrup Christoffersen, Johan Broersma, Magnus Lindholm Nielsen, Mandy Hazenberg, María Coto Sarmiento, Paulina Fulneczek, Petra Hermankova, Ties Heesink. We also want to thank all the participants of our workshops.
